Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
Making notation consistent and porting polytopes notes.

The base object of study is a \emph{discrete loss function} $\ell: \R \to \nonnegreals^{\Y}$ where $\R$ and $\Y$ are finite sets.
Here $\ell(r)_y$ is the loss of prediction $r \in \R$ (the report space) on $y \in \Y$ (the observation or label space).
For simplicity we let $\Y = [n]$ throughout (where $[n] = \{1,\ldots,n\}$).
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\nonnegreals^{\Y}$, represented as vectors of probabilities.
We write $p(y)$ \bo{check/decide}\jessie{Fine with this, and I think it's consistently in the paper like this already} for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report $r$ uniquely minimizes expected loss for some distribution $p\in\simplex$.

@@

\paragraph{Properties of distributions.}
In order to study calibration of surrogates (Definition~\ref{def:calibration} below), it is useful to formalize the following functions that describe the reports that minimize expected $\ell$-loss and $L$-loss under $p$.
%% Bo: since we use \gamma and \R for \ell, and we use \Gamma and \reals^d for L,
%% I figured generic properties could use notation g and R for f
\begin{definition}[(Finite) property, level set, elicited]
  A \emph{property} is a function $g: \simplex \to 2^{R}$ for some set $R$ where $g(p) \neq \emptyset$ for all $p$.
  It is \emph{finite} if $|R| < \infty$.
  The \emph{level set} of $r \in R$ is the set $g_r = \{p \in \simplex : r \in g(p)\}$.
  A loss function $f: R \to \nonnegreals^{\Y}$ \emph{elicits} $g$ if $g(p) = \argmin_{r \in R} \inprod{p}{f(r)}$.
  We assume all properties are non-redundant, i.e. each $g_r$ contains a distribution $p$ not in any other $g_{r'}$.\jessiet{$R$ or $\R$?}
\end{definition}
For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $R = \Y$ via $g(p) = \argmax_{y \in \Y} p(y)$.
Notice in this example $g(p)$ is a singleton set when the mode of $p$ is unique and e.g. is $\Y$ when $p$ is uniform.
%Another example of a finite property is ranking, in which $\R$ is the set of permutations of $\Y$, and $g(p)$ consists of all permutations that order $\Y$ from most to least probable (i.e. ties must be broken in all possible ways).
In this paper we write $\gamma$ for the property elicited by $\ell$ with report space $\R$; and we use $\Gamma$ for the property elicited by $L$ with report space $\reals^d$.

@@

  Given a distribution $p \in \simplex$, we write the $p$-weighted Minkowski sum of $\T$ as
    \[ \oplus_p \T := \left\{ \sum_{y \in \Y} p(y) x_y ~\Big|~ x_1 \in T_1, \dots, x_y \in T_y \right\} , \]
  in other words, the Minkowski sum of the scaled sets $\{p(y) T_y : y \in \Y\}$.

@@

\begin{theorem} \label{thm:general-char}
  Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r)}\}$.
  Then $\ell$ is $d$-embeddable if and only if there exists a collection of polytopes $\T^r = \{T^r_y : y \in \Y\}$ for each $r \in \R$ such that both of the following hold:
  \begin{enumerate}
    \item (Optimality) For each $r$, we have $D(\T^r) = \gamma_r$.
    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $r \in \R$ and $y \in \Y$, we have $T^r_y = \partial L_y(\varphi(r))$ and for all $r \in \R$, we have $L_y(\varphi(r)) = \ell_y(r)$.
  \end{enumerate}
\end{theorem}
\begin{proof}
  \jessie{An attempt:}
  $(\implies)$ If $\ell$ is $d$-embeddable, say that $L:\reals^d \to \reals^\Y_{\geq 0}$ embeds $\ell$.
  Take $T_y$ to be $\partial L(\varphi(r))_y$ for a fixed $r \in \R$ and $y \in \Y$.
  Clearly this set of polytopes $\T$ satisfies the monotonicity condition.
  To see the optimality condition is satisfied, consider that $\gamma_r = \Gamma_{\varphi(r)} = \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : \vec 0 \in \oplus_p T_y \} = D(\T)$.

@@

To gain a better understanding about the QFP in Definition~\ref{def:qfp}, we prove the following:
\begin{lemma} \label{lemma:D-polytope}
  For any $\T$, $D(\T)$ is a polytope (in particular, is convex).
\end{lemma}
\begin{proof}
  \jessie{Appendix}
   Recall by definition, the notation $\oplus_p \T = \{\sum_y p(y) x_y : x_y \in T_y (\forall y)\}$.
   Each $T_y$ is a polytope, so $p(y) T_y$ is a polytope.
   The Minkowski sum of polytopes is a polytope, so $\oplus_p \T$ is a polytope by~\cite[Section 1.2]{weibel2007minkowski}.
  \bo{TODO}\jessie{Taking a try}
  Since $\oplus_p \T$ is a polytope for all $p \in \simplex$, we know there is a halfspace representation of normals $V$ so that for all $y \in \Y$, we have $x \in p(y)T_y \iff \inprod{V}{x} \leq p(y) e^y$ for some matrix $V$ and the support vector $e^y$, where $e^y_i = H_{T_y}(V_i)$.
  Adding redundant constraints for the $e^y$ as necessary, we know that the support of the Minkowski sum for a given normal is the sum of the normals~\cite[Theorem 3.1.6]{weibel2007minkowski}.
  Concatenating the vectors $e^y$ into $E$, we have $x \in \oplus_p \T \iff \inprod{V^*}{x} \leq E^*p$, where $V^*$ has redundant rows added as necessary. \jessie{Hand wavy... not a fan.}
  Substituting $x = \vec 0$, we see $\vec 0 \in \oplus_p \T \iff Ep \geq \vec 0$, which defines a polytope by construction of $E$.
\end{proof}
\begin{lemma}  \label{lemma:minkowski-support}
  Given polytopes $\T$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p(y) \max_{x \in T_y} \inprod{w_i}{x} \}$.
\end{lemma}
\begin{proof}
  \jessie{Appendix}
   For each $p$, $\oplus_p \T$ is a polytope.
  \bo{TODO: it turns out that $p$ doesn't matter, only its support; and there are only finitely many possible supports (or even better, the normals that are complete for the uniform minkowski sum turn out to be complete for all other $p$-combinations).}
  For each of the finitely many supports ($2^n - 1$), we know $\oplus_p \T$ is a polytope, and every polytope can be uniquely defined by an enumeration of vectors normal to its facets.
  As a two polytopes with the same support can be defined by the same facet enumeration, we can simply concatenate these finite set of normals for the finite polytope supports.
  Vectors that are not normal to a facet simply become redundant constraints.
  This yields finitely many normals defining the weighted Minkowski sum $\oplus_p \T$ for all $p \in \simplex$.
\end{proof}
\begin{lemma} \label{lemma:E-to-B}
  Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
  Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
\end{lemma}
\begin{proof}
  \bo{? Cite} \jessie{Is left as an exercise in the following text:} \cite[Exercise 2.15]{ziegler2012lectures}
\end{proof}

@@

  By Lemma \ref{lemma:minkowski-support}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ and such that $\vec 0 \in \oplus_p \T$ if and only if, for all $w_i$, $\sum_y p(y) \max_{x \in T_y} \inprod{w_i}{x} \geq 0$.
  Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T_y} \inprod{w_i}{x}$, and we have $p \in D(\T) \iff Ep \geq 0$.
  By assumption of $D(\T) = C$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
  By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$. Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors that we can rename $v_1,\ldots,v_k \in \reals^d$, with $\max_{x \in T_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.

  ($\impliedby$)
  Suppose Conditions \ref{cond:H-condition} and \ref{cond:V-condition} hold.
  Then by the vertex condition, $p^j \in D(\T)$ for all $j \in [\ell]$.
  Because $D(\T)$ is convex (Lemma \ref{lemma:D-polytope}), this implies $C \subseteq D(\T)$.
  To show $D(\T) \subseteq C$, let $p \in D(\T)$; by definition, $0 \in \oplus_p \T$.
  Then in particular for each vector $v_1,\ldots,v_k$ guaranteed by the halfspace condition, we have
  \begin{align*}
    0 &\leq \max_{x \in \oplus_p \T} \inprod{v}{x}  \\
      &=    \sum_{y \in \Y} p(y) \max_{x \in T_y} \inprod{v_i}{x}  \\
      &\leq \sum_{y \in \Y} p(y) B_{iy} .
  \end{align*}
  This proves $Bp \geq 0$, so $p \in C$.
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Example: Abstain loss}\label{sec:examples}
\subsection{Abstain, $d=1$}\label{subsec:abstain-d1}
One classification-like problem that is of particular interest is the abstain property, elicited by the loss $\ellabs{\alpha}$ given in Equation~\eqref{eq:abstain}.
The property $\gamma = \abstain{\alpha}$ for $\alpha \in (0,1)$ can be verified:
\begin{equation}\label{eq:abstain-prop}
     \abstain{\alpha}(p) = \begin{cases}
     \argmax_{y \in \Y} p(y) & \max_y p(y) \geq 1 - \alpha\\
     \bot & \text{otherwise}
     \end{cases}~.~
\end{equation}

@@

\begin{proposition}\label{prop:qfp-fails-abstain}
  The quadratic feasibility program (Definition \ref{def:qfp}) with input $C = \gamma_{\bot} = \{p \in \simplex: \max_y p(y) \leq 1/2\}$, $n=5$, and dimension parameter $d=2$, is infeasible.
\end{proposition}
\begin{corollary}
  The abstain loss with $\alpha=1/2$ on $5$ outcomes is not $2$-embeddable.
\end{corollary}

@@

\section{$d$-dimensional omitted proofs}

>>>>

The base object of study is a \emph{discrete loss function} $\ell: \R \to \nonnegreals^{\Y}$ where $\R$ and $\Y$ are finite sets.
Here $\ell(r)_y$ is the loss of prediction $r \in \R$ (the report space) on $y \in \Y$ (the observation or label space).
For simplicity we let $\Y = [n]$ throughout (where $[n] = \{1,\ldots,n\}$).
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\nonnegreals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ \bo{check/decide}\jessie{Fine with this, and I think it's consistently in the paper like this already} for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
As is assumed by~\cite{finocchiaro2019embedding}, we assume the given discrete loss is \emph{non-redundant}, meaning every report $r$ uniquely minimizes expected loss for some distribution $p\in\simplex$.

@@

\paragraph{Properties of distributions.}
In order to study calibration of surrogates (Definition~\ref{def:calibration} below), it is useful to formalize the following functions that describe the reports that minimize expected $\ell$-loss and $L$-loss under $p$.
%% Bo: since we use \gamma and \R for \ell, and we use \Gamma and \reals^d for L,
%% I figured generic properties could use notation g and R for f
\begin{definition}[(Finite) property, level set, elicited]
  A \emph{property} is a function $g: \simplex \to 2^{R}$ for some set $R$ where $g(p) \neq \emptyset$ for all $p$.
  It is \emph{finite} if $|R| < \infty$.
  The \emph{level set} of $r \in R$ is the set $g_r = \{p \in \simplex : r \in g(p)\}$.
  A loss function $f: R \to \nonnegreals^{\Y}$ \emph{elicits} $g$ if $g(p) = \argmin_{r \in R} \inprod{p}{f(r)}$.
  We assume all properties are non-redundant, i.e. each $g_r$ contains a distribution $p$ not in any other $g_{r'}$.\jessiet{$R$ or $\R$?}
\end{definition}
For example, $0-1$ loss elicits the mode, which is formalized as a property on report space $R = \Y$ via $g(p) = \argmax_{y \in \Y} p_y$.
Notice in this example $g(p)$ is a singleton set when the mode of $p$ is unique and e.g. is $\Y$ when $p$ is uniform.
%Another example of a finite property is ranking, in which $\R$ is the set of permutations of $\Y$, and $g(p)$ consists of all permutations that order $\Y$ from most to least probable (i.e. ties must be broken in all possible ways).
In this paper we write $\gamma$ for the property elicited by $\ell$ with report space $\R$; and we use $\Gamma$ for the property elicited by $L$ with report space $\reals^d$.

@@

  Given a distribution $p \in \simplex$, we write the $p$-weighted Minkowski sum of $\T$ as
    \[ \oplus_p \T := \left\{ \sum_{y \in \Y} p_y x_y ~\Big|~ x_1 \in T_1, \dots, x_y \in T_y \right\} , \]
  in other words, the Minkowski sum of the scaled sets $\{p_y T_y : y \in \Y\}$.

@@

\begin{theorem} \label{thm:general-char}
  Let $\ell: \R \to \reals_{\geq 0}^{\Y}$ be a discrete loss with, for each $r \in \R$, $\gamma_r = \{p : r \in \argmin_{r'} \inprod{p}{\ell(r)}\}$.
  Then $\ell$ is $d$-embeddable if and only if there exists a collection of polytopes $\T^r = \{T^r_y : y \in \Y\}$ for each $r \in \R$ such that both of the following hold:
  \begin{enumerate}
    \item (Optimality) For each $r$, we have $D(\T^r) = \gamma_r$.
    \item (Monotonicity) There exists an injective embedding function $\varphi : \R \to \reals^d$ and loss functions $\{L_y : \reals^d \to \reals^\Y_{\geq 0}\}_{y \in \Y}$ such that for all $r \in \R$ and $y \in \Y$, we have $T^r_y = \partial L(\varphi(r))_y$ and for all $r \in \R$, we have $L(\varphi(r))_y = \ell(r)_y$.
  \end{enumerate}
\end{theorem}
\begin{proof}
  \jessie{An attempt:}
  $(\implies)$ If $\ell$ is $d$-embeddable, say that $L:\reals^d \to \reals^\Y_{\geq 0}$ embeds $\ell$.
  Take $T_y$ to be $\partial L(\varphi(r))_y$ for a fixed $r \in \R$ and $y \in \Y$.
  Clearly this set of polytopes $\T$ satisfies the monotonicity condition.
  To see the optimality condition is satisfied, consider that $\gamma_r = \Gamma_{\varphi(r)} = \{p \in \simplex : \vec 0 \in \oplus_p \partial L(\varphi(r))_y \} = \{p : \vec 0 \in \oplus_p T_y \} = D(\T)$.

@@

To gain a better understanding about the QFP in Definition~\ref{def:qfp}, we prove the following in Appendix~\ref{app:omitted-d-dim}:
\begin{lemma}  \label{lemma:minkowski-support}
	Given polytopes $\T$, there exists a finite set of normal vectors $w_1,\ldots,w_K \in \reals^d$ such that, for all $p \in \simplex$, $\oplus_p \T = \{x : \inprod{w_i}{x} \leq \sum_{y \in \Y} p_y \max_{x \in T_y} \inprod{w_i}{x} \}$.
\end{lemma}

\begin{lemma} \label{lemma:D-polytope}
  For any $\T$, $D(\T)$ is a polytope (in particular, is convex).
\end{lemma}

\begin{lemma} \label{lemma:E-to-B}
  Let $C = \{p : Bp \geq \vec 0 \}$ where $B$ has the minimum possible number of rows to capture $C$, and suppose $C = \{p : Ep \geq \vec 0 \}$.
  Then for each row in $B$ there is some (unique) row in $E$ that is equal to $\alpha B$ for some positive $\alpha$.
\end{lemma}

@@

  By Lemma \ref{lemma:minkowski-support}, there is a finite collection of vectors $w_1,\dots,w_{K} \in \reals^d$ and such that $\vec 0 \in \oplus_p \T$ if and only if, for all $w_i$, $\sum_y p_y \max_{x \in T_y} \inprod{w_i}{x} \geq 0$.
  Hence, each vector $w_i$ generates a row of a matrix $E \in \reals^{K \times n}$ with $E_{iy} = \max_{x \in T_y} \inprod{w_i}{x}$, and we have $p \in D(\T) \iff Ep \geq 0$.
  By assumption of $D(\T) = C$, then, we have $Ep \geq 0 \iff Bp \geq 0$.
  By Lemma \ref{lemma:E-to-B}, because $B$ has the minimum possible number of rows, each row of $B$ appears (scaled by some positive constant) as a different row of $E$. Taking the collection of $w_i$ corresponding to these rows and rescaling them by that positive constant, we get a collection of $k$ vectors that we can rename $v_1,\ldots,v_k \in \reals^d$, with $\max_{x \in T_y} \inprod{v_i}{x} = B_{iy}$, hence the halfspace condition is satisfied.

  ($\impliedby$)
  Suppose Conditions \ref{cond:H-condition} and \ref{cond:V-condition} hold.
  Then by the vertex condition, $p^j \in D(\T)$ for all $j \in [\ell]$.
  Because $D(\T)$ is convex (Lemma \ref{lemma:D-polytope}), this implies $C \subseteq D(\T)$.
  To show $D(\T) \subseteq C$, let $p \in D(\T)$; by definition, $0 \in \oplus_p \T$.
  Then in particular for each vector $v_1,\ldots,v_k$ guaranteed by the halfspace condition, we have
  \begin{align*}
    0 &\leq \max_{x \in \oplus_p \T} \inprod{v}{x}  \\
      &=    \sum_{y \in \Y} p_y \max_{x \in T_y} \inprod{v_i}{x}  \\
      &\leq \sum_{y \in \Y} p_y B_{iy} .
  \end{align*}
  This proves $Bp \geq 0$, so $p \in C$.
\end{proof}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Example: Abstain loss}\label{sec:examples}
\subsection{Abstain, $d=1$}\label{subsec:abstain-d1}
One classification-like problem that is of particular interest is the abstain property, elicited by the loss $\ellabs{\alpha}$ given in Equation~\eqref{eq:abstain}.
The property $\gamma = \abstain{\alpha}$ for $\alpha \in (0,1)$ can be verified:
\begin{equation}\label{eq:abstain-prop}
     \abstain{\alpha}(p) = \begin{cases}
     \argmax_{y \in \Y} p_y & \max_y p_y \geq 1 - \alpha\\
     \bot & \text{otherwise}
     \end{cases}~.~
\end{equation}

@@

\begin{proposition}\label{prop:qfp-fails-abstain}
  The quadratic feasibility program (Definition \ref{def:qfp}) with input $C = \gamma_{\bot} = \{p \in \simplex: \max_y p_y \leq 1/2\}$, $n=5$, and dimension parameter $d=2$, is infeasible.
\end{proposition}
\begin{corollary}
  The abstain loss with $\alpha=1/2$ on $5$ outcomes is not $2$-embeddable.
\end{corollary}

@@

\section{Polytope notes}
Here, we recall some standard definitions from the theory of Convex Polytopes.
\begin{definition}
	A \emph{polyhedra} in $\reals^d$ is defined by the intersection of a finite number of half-spaces.
	A \emph{polytope} is a bounded polyhedra.
\end{definition}

\begin{definition}[Valid inequality]
	Let $S$ be a set in $\reals^d$.
	A \emph{valid inequality} for $S$ is an inequality that holds for all vectors in $S$.
	That is, the pair $(a,\beta)$ is a valid inequality for $S$ if and only if 
	\begin{align*}
	\inprod{a}{x} &\leq \beta \; \; \forall x \in S~.~
	\end{align*}
\end{definition}

\begin{definition}[Face]\label{def:face}
	For any valid inequality of a polytope, the subset of the polytope of vectors which are tight for the inequality is called a \emph{face} of the polytope.
	That is, the set $F$ is a face of the polytope $T$ if and only if 
	\begin{align*}
	F &= \{x \in T : \inprod{a}{x} = \beta \}
	\end{align*}
	for some valid inequality $(a, \beta)$ of $T$.
\end{definition}

\begin{definition}[Supporting function]
	Let $S$ be a nonempty bounded set in $\reals^d$.
	We call the \emph{supporting function} of $S$ the function $H_S:\reals^d \to \reals$ by
	\begin{align*}
	H_S(a) := \sup_{x \in S}\inprod{a}{x}~.~
	\end{align*} 
\end{definition}

\iffalse
\begin{definition}[Maximizers]
	Let $S \subseteq \reals^d$, and $a \in \reals^d$.
	The \emph{set of maximizers} of $a$ over $S$ is defined as
	\begin{align*}
	\mathcal{S}(S;a) &= \{x \in S : \inprod a x = H_S(a)\}
	\end{align*}
\end{definition}

\begin{definition}[Normal cones]
	Let $T$ be a polytope in $\reals^d$.
	For any face $F$ of $T$, we define its \emph{normal cone} $\N(F;T)$ as the set of vectors for which $F$ is the maximizer set over $T$.
	That is,
	\begin{align*}
	\N(F;T) = \left\{a : F = \mathcal{S}(T; a) \right\}~.~
	\end{align*}
\end{definition}

It is worth noting that normal cones are generally not closed by this definition, but sometimes we may want to think about the closure of the normal cone.
\fi

\begin{definition}[Minkowski sum]
	Let $S_1, S_2, \ldots, S_n$ be sets of vectors.
	We can define their \emph{Minkowski sum} as the set of vectors which can be written as the sum of a vector in each set.
	Namely,
	\begin{align*}
	S_1 \oplus \ldots \oplus S_n &= \{x_1 + \ldots + x_n : x_i \in S_i \; \forall i \}
	\end{align*}
\end{definition}

%\begin{theorem}[\cite[Theorem 3.1.2]{weibel2007minkowski}] \label{thm:unique-face-decomp}
%	Let $T_1, \ldots, T_n$ be polytopes in $\reals^d$ and let $F$ be a face of the Minkowski sum $T := T_1 \oplus \ldots \oplus T_n$.
%	Then there are faces $F_1, \ldots, F_n$ of $T_1, \ldots, T_n$ respectively such that $F = F_1 \oplus \ldots \oplus F_n$.
%	Moreover, this decomposition is unique.
%\end{theorem}

\iffalse 
\begin{corollary}[\cite[Corollary 3.1.3]{weibel2007minkowski}]\label{cor:face-decomp-normal-cones}
	Let $T = T_1 \oplus \ldots \oplus T_n$ be a Minkowski sum of polytopes in $\reals^d$, let $F$ be a nonempty face of $T$ , and let $F_1, \ldots, F_n$ be its decomposition.
	Then $\N(F;T) = \N(F_1;T_1) \cap \ldots \cap \N(F_n; T_n)$.
\end{corollary}

%used in proving completeness of constructed V
\begin{corollary}[\cite[Corollary 3.1.4]{weibel2007minkowski}]
	Let $F_1, \ldots, F_n$ be nonempty faces of the polytopes $T_1, \ldots, T_n$ respectively, then $F_1 \oplus \ldots \oplus F_n$ is a face of $T_1 \oplus \ldots \oplus T_n$ if and only if the intersection of their normal cones is nonempty.
\end{corollary}
\fi

%\begin{theorem}[\cite[Theorem 3.1.6]{weibel2007minkowski}]\label{thm:support-minksum}
%	The supporting function of a Minkowski sum is the sum of the supporting functions of its summands.
%\end{theorem}

\begin{definition}[Weighted Minkowski sum]
	If $T_1, \ldots, T_n$ are polytopes in $\reals^d$, we can call $T(\vec p)$ their \emph{weighted} Minkowski sum for $\vec p \in \reals^n_{\geq 0}$,
	\begin{align*}
	T(\vec p) &:= \oplus_y p_y T_y = p_1 T_1 \oplus \ldots \oplus p_n T_n
	\end{align*}
\end{definition}

%From the thesis:  \emph{``It is easy to see that the normal fan (undefined here, but consequently normal cones) of $p_i T_i$ does not change as long as $p_i$ is positive.  Since the normal fan of a Minkowski sum can be deduced from that of its summands, we can deduce from this that the conbimatorial properties of $\oplus_y p_y T_y$ stay the same as long as all $p_i$ are positive.''}

Suppose we are given a polytope $T_y \in \reals^d$ and set of vectors $V \in \reals^{k \times d}$.
Call $e^y \in \reals^k$ the vector such that $e^y_i = \max_{x \in T_y}\inprod{v_i}{x}$.  
For a finite set $\T = \{T_1, , \ldots, T_n\}$, let us denote the \emph{support matrix} $E = (e^y)_{y=1}^n$.
\begin{definition}
	We say a set of normals $V$ is \emph{complete} with respect to a polytope $T_y$ if $T_y = \{x \in \reals^d: Vx \leq e^y\}$.
\end{definition}
Moreover, we say $V$ is complete with respect to the set of polytopes $\T$ if and only if $V$ is complete with respect to each $T_y \in \T$.

\subsubsection*{Optimality Condition}
In general, we know that $\vec 0$ in the subgradient of $f(r)$ if and only if $r$ is an optimum of convex $f$ in general dimensions.

For nice\footnote{for reports on the relative interior of the domain, and something else} conditions, we have $\vec 0 \in \oplus_i f_i$ if and only if $\vec 0 \in \oplus_i \partial f_i(r)$.
This allows us to consider the following optimality condition:
\begin{definition}\label{def:optimality}[Optimality]
	For all $r \in \R$ and $y \in \Y$, we have $r \in \gamma_r \iff \vec 0 \in \oplus_y p_y T_y(r)$.
\end{definition}
The polytope $T_y(r)$ can be thought of as $\partial L_y(\varphi(r))$.

We will suppose we start with a finite set of $n$ polytopes $\T := \{T_1, \ldots, T_n\}$, and we will call $T := T_1 \oplus \ldots \oplus T_n \in \reals^d$ their Minkowski sum.
We know that every polytope has both a halfspace and vertex representation ($\H$-representation and $\V$-representation, respectively.)
By existence of the $\H$-representation, we know there must be a matrix $V \in \reals^{k \times d}$ and vector $e \in \reals^k$ such that $T = \{x \in \reals^d : Vx \leq e\}$.
In fact, with a complete set of normals $V$, we know that $e$ can be the support vector of each of the normals.
However, finding $V$ is not always easy, so we assume that we are given $V$ for now.

\subsection{Given normals $V$}
Now, for a given polytope $T(p)$, we want to ask when a given $z \in \reals^d$ is in the polytope $T(p)$.
We will later generalize to finding the set of $p \in \simplex$ for which $\vec 0 \in T(p)$ by substituting $z= \vec 0$.
Throughout, assume we have $V$ which is complete for $\T$ and $E$ defined by the support of each normal in $V$ for all $T_y \in \T$.
We denote $e^y = E_{;y}$ as the $y^{th}$ column of $E$, or equivalently, the support vector for $T_y$ given $V$.

Since we define $T_y = \{x : Vx \leq e^y\}$, we can multiply the right side of the inequality by the constant $p_y \geq  0$ to yield $p_y T_y = \{x : Vx \leq p_y e^y\}$.
Taking the Minkowski sum of polytopes described by the same set of normals, we can take 
\begin{align*}
\oplus_y p_y T_y &= \{x : Vx \leq p_1 E_{;1}\} \oplus \ldots \oplus \{x : Vx \leq p_n E_{;n}\} \\
&= \{x : Vx \leq p_1 E_{;1} + \ldots + p_n E_{;n}\}\\
&= \{x : Vx \leq E p\}~.~
\end{align*}
The first to second line follows from Theorem~\ref{thm:support-minksum} and preservation of inequalities under addition.
Now, we have $z \in T(p) \iff \inprod{v_i}{z} \leq (Ep)_i$ for all $v_i \in V$.

Observe that we have $\vec 0 \in T(p)$ if and only if $E p \geq 0$ by substitution, which lines up with our optimality condition in Definition~\ref{def:optimality}.

We assume $p \in \simplex$, so we now describe the cell $D^\T := \{p \in \simplex : Ep \geq \vec 0\}$ as the set of distributions such that $\vec 0 \in T(p)$.
In cases where $\T$ is obvious from context, we omit the subscript and just write $D$.

Given the complete set of normals $V$ and constructing the support matrix for $V$ and $\T$, $E$, we observe that $E$ is unique up to rescaling.
However, as discussed earlier, there are always multiple complete sets of normals for $\T$, and so in that sense, $E$ is not unique.

\subsection{Equivalences}
In the big picture, we want to know two things.
First, if we are given a cell $C$, how we can construct a finite set of polytopes $\T = \{T_1, \ldots, T_n\}$ such that $\vec 0 \in T(p) \iff p \in C$.
Second, we want to know the opposite case: starting from $\T$, can we derive the cell $C \subseteq \simplex$ where $\vec 0 \in T(p)$ for all $p \in C$?
We start with the latter, leaving the former for future work.

We know that if we are given $\T$ and a complete set of normals $V$, we can describe $D = \{p \in \simplex : Ep \geq \vec 0\}$ as in Section~\ref{sec:start-polytope}.
However, we do not necessarily have $D' := \{p \in A : Ep \geq \vec 0\} \subseteq \simplex$, and this poses some issues given the construction of the cell $C$ only assuming that we are in the affine span of the simplex, but not necessarily in the simplex.

\begin{lemma}\label{lem:describe-D}
	Suppose we are given polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and $D^\T = \{p \in \simplex : Ep \geq \vec 0\}$.

	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = \{p \in \simplex: Ep \geq \vec 0\}$.\btw{on the whiteboard: ``stuff about $E$ and $D$.''}
\end{lemma}
\begin{proof}
	First, let us fix a distribution $p \in \simplex$.
	By Theorem~\ref{thm:support-minksum}, we have the support of the (weighted) Minkowski sum is the (weighted) sum of the support of each polytope, which we can re-write the weighted support as the product $Ep$.

	Each halfspace is bounded by the support function of the weighted polytope by construction of $E$, so the support of the weighted polytope defined by an inequality on $v_i$ can be described as $\inprod{v_i}{z} \leq \inprod{E_i}{p}$.
	Taking this for all $v_i$, we then have $\oplus_y p_y T_y = \{x \in \reals^d : Vx \leq Ep\}$.

	Therefore, for fixed $p$, we have $\vec 0 \in \oplus_y p_y T_y \iff Ep \geq \vec 0$.
	As $p \in \simplex$ was arbitrary, we observe the stated set equality.
\end{proof}

\begin{proposition}\label{prop:relate-E-B}
	Suppose we are given polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
	Take $E = (e_{iy})$ where $e_{iy} = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and take the minimal rank $B \in \reals^{k \times n}$ such that we have the given cell $C = \{p \in \simplex : Bp \geq \vec 0\}$.

	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only if $C = D$.
\end{proposition}
\begin{proof}
	By Lemma~\ref{lem:describe-D}, we have $D = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$, and the result follows.
\end{proof}

\begin{definition}
	We say a vector $v$ is \emph{redundant} with respect to matrix $Y$ if we have $\{z: Yz \geq \vec b\} = \{z : [Y;v]z \geq \vec b^*\}$, where $b^* = [b;c]$ for some constant $c \in \reals$.
\end{definition}

\begin{proposition}\label{prop:relate-rows}
	Suppose we have polytopes $\T = \{T_1, \ldots, T_n\}$ and a set of normals $V$ that is complete for $\T$.
	Take $E = (e_{i}^y)$ where $e_{i}^y = \max_{x \in T_y} \inprod{v_i}{x}$, and take $D = \{p \in \simplex : Ep \geq \vec 0\}$ and take the minimal matrix $B$ such that a given cell $C = \{p \in \simplex : Bp \geq \vec 0\}$.

	Then $\{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\} = C$	if and only the rows of $B$ appear in $E$ (possibly scaled) and every other row of $E$ is redundant with respect to $B$.
	\btw{``replace prop 1 statement with `non-simplex rows of $B$ appear in $E$ (possible scaled) and every other row of $E$ is redundant with respect to $B$.'''}
\end{proposition}
\begin{proof}
	\begin{itemize}
		\item [$\implies$] First, assume $C = \{p \in \simplex: \vec 0 \in \oplus_y p_y T_y\}$.
		By Proposition~\ref{prop:relate-E-B}, we know that $C = D^\T := \{p \in \simplex : Ep \geq \vec 0\}$.
		Then we have $\{p \in \simplex : Bp \geq \vec 0\} = \{p \in \simplex : Ep \geq \vec 0\}$.
		As $B$ is minimal, we must have that every row of $B$ appears (possibly scaled) in $E$.
		Otherwise, we would contradict equality of the polytopes $C$ and $D$.
		Moreover, all rows in $E$ not in $B$ are redundant with respect to $B$ by equality of the polytopes.

		\item [$\impliedby$] Suppose that all rows of $B$ appear in $E$, and every other row of $E$ is redundant with respect to $B$.
		Then we have $D = \{p\in \simplex : Ep \geq \vec 0\} = \{p \in \simplex : Bp \geq \vec 0\} = C$.

		Then $D = C$, and by Proposition~\ref{prop:relate-E-B}, we have $C = \{p \in \simplex : \vec 0 \in \oplus_y p_y T_y\}$.
	\end{itemize}
\end{proof}
